Carbonate chemistry at Ny-Ålesund

### 2021-08-24 awipev-CO2.Rmd
Takahashi thermal vs non-thermal finalized
revised ranges

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(montht) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
kable(range_month, caption = "")
```

>>>>

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
                                   med = ~ median(., na.rm = TRUE),
                                   min = ~ min(., na.rm = TRUE),
                                   max = ~ max(., na.rm = TRUE),
                                   q5 = ~ quantile(., 0.05, na.rm = TRUE),
                                   q95 = ~ quantile(., 0.95, na.rm = TRUE)
                                   ), 
                     append = FALSE)

range_month <-
  d_all %>%
  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_9m) %>% 
  group_by(montht) %>%
  my_skim()
kable(range_month, caption = "")
```
